Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-12-13 script/manuscript_MEE.Rmd
forget to push somewriting

output:
  pdf_document: default
  toc: no
  word_document: default
csl: "../citations/methods-in-ecology-and-evolution.csl"
bibliography: ../citations/citations.bib
link-citations: yes
fig_caption: yes
always_allow_html: true
header-includes:
- \usepackage{endfloat}
- \usepackage{setspace}\doublespacing
- \usepackage{lineno}
- \linenumbers
---

@@

  Recently barcoding (the identification of a sample from a single organism – e.g. a piece of leaf), and metabarcoding (the identification of a sample containing a mix of organisms – e.g. soil), have shown considerable promise in all Kingdoms of life (@ruppert2019past). With plants the identification of members of certain clades using barcoding has been quite successful (REF), whereas with others results have been elusive (@liu2014identification, @china2011comparative, @coissac2012bioinformatic), however metabarcoding incurs additional challenges to those which  exist for the currently implemented barcodes (@li2015plant, @kress2007two, @cbol2009dna, @coissac2012bioinformatic). Particular challenges with barcodes include the utilization of high-copy number sequences are associated with their rates of divergence, gene tree conflict, and hybridization (@coissac2016barcodes, @fazekas2009plant). Particular challenges with the utilization of high-copy number sequences are associated with their rates of divergence, gene tree conflict, and hybridization (@coissac2016barcodes).

@@

  Considerable amounts of species interactions vary along time (@caradonna2021seeing). For the tropics, contrasts in the flowering periods of many plant species, can provide an additional filter for identifying material in many metagenomic samples (@janzen1967synchronization, @Newstrom1994ANC). In temperate regions, pollination interactions also vary temporally (@caradonna2017interaction), the overall shorter extent of the active growing season in these systems results in the presence of few to any natural breaks in these systems which subjugates the utility of these to perform as filters of post-processing results, rather than distinct species assemblage for database generation. Nonetheless, we work through a process which seems applicable to the tropics to utilize the temporal dimension for classifying sequencing results.

  We apply these metagenomic and informatics approaches to determine whether the foraging record of Queen Bumble Bee's is consistent across direct observations and the pollen record, an incongruency in several floral visitation networks (@barker2021pollen, @zhao2019topology, @alarcon2010congruence). The two foraging phases of the Queen Bumble Bee life cycle is essential to 1) increase their weight before diapause, 2) increase their ovary weights while establishing their recently found nests, both of these time periods represent potential demographic bottlenecks in bumble bee populations (@sarro2022bumble). Bumblebees are one of the only groups of insects with unequivocal quantitative evidence for numerous populations declines, while simultaneously serving as the most effective pollinators in temperate montane ecosystems (@cameron2020global, @goulson2008decline, @williams1982distribution, @colla2012assessing, @bergman1996micrometeorological, @bingham1998efficient). These montane ecosystems represent some of the most ecologically resilient and resistant systems in the temperate and offer unparalleled potential as refugial areas for multiple dimensions of biodiversity under climate change.

@@

@@

The first date of modeled snow melt in the Gothic area (n = 17, $\bar{x}$ = 137.9, Mdn = 135, 3rd quantile = 151), and the first date of a consistent winter snow base (n = 17, $\bar{x}$ = 299.9, Mdn = 300, 1st quantile = 291) from 2000-2017, were used as delimiters for the inclusions of herbarium records in modelling. Of the **500** species predicted likely present in the area via logistic regression, 332 species (64.4%) with more than 10 records in the focal level 4 ecoregions ($\bar{x}$ = 35.01657, Mdn = 35, max = 96) had weibull estimates calculated, an additional 56 species (11.2%) with enough contributing records from the 'Sedimentary Mid-Elevation Forests', a large ecoregion in general just beneath the elevation bands occupied by the five ecoregions around the study area had weibull estimates also calculated ($\bar{x}$ = 13.86885, Mdn = 13, max = 24).

@@

@@

@@

@@

>>>>

output:
  word_document: default
  toc: no
  pdf_document: default
csl: "../citations/methods-in-ecology-and-evolution.csl"
bibliography: ../citations/citations.bib
link-citations: yes
fig_caption: yes
always_allow_html: true
header-includes:
- \usepackage{endfloat}
- \usepackage{setspace}\doublespacing
- \usepackage{lineno}
- \linenumbers
---

@@

  Recently barcoding (the identification of a sample from a single organism *e.g.* a piece of leaf), and metabarcoding (the identification of a sample containing a mix of organisms *e.g.* soil), have shown considerable promise in all Kingdoms of life (@ruppert2019past). With plants the identification of members of certain clades using barcoding has been quite successful (REF), whereas with other clades results have been elusive (@liu2014identification, @china2011comparative, @coissac2012bioinformatic), however metabarcoding incurs additional challenges to those which  exist for the currently implemented barcodes (@li2015plant, @kress2007two, @cbol2009dna, @coissac2012bioinformatic). Particular challenges with barcodes include the utilization of high-copy number sequences are associated with their rates of divergence, gene tree conflict, and hybridization (@coissac2016barcodes, @fazekas2009plant). Particular challenges with the utilization of high-copy number sequences are associated with their rates of divergence, gene tree conflict, and hybridization (@coissac2016barcodes).

@@

  Considerable amounts of species interactions vary along time (@caradonna2021seeing). For the tropics and subtropics, contrasts in the flowering periods of many plant species, can provide an additional filter for identifying material in many metagenomic samples (@janzen1967synchronization, @Newstrom1994ANC). In temperate regions, pollination interactions also vary temporally (@caradonna2017interaction), however the overall shorter extent of the active growing season in these systems results in the presence of few to any natural breaks in these systems which reduces the utility of these to operate as filters in the post-processing of sequence matches. Nonetheless, we work through a process which seems applicable to the tropics and subtropics to utilize the temporal dimension for classifying sequencing results.

  We apply these metagenomic and informatics approaches to determine whether the foraging record of Queen Bumble Bee's is consistent across direct observations and the pollen record, an incongruency in several floral visitation networks involving smaller bodied fauna (@barker2021pollen, @zhao2019topology, @alarcon2010congruence). The two foraging phases of the Queen Bumble Bee life cycle is essential to 1) increase their weight before diapause, 2) increase their ovary weights while establishing their recently found nests, both of these time periods represent potential demographic bottlenecks in bumble bee populations (@sarro2022bumble). Bumblebees are one of the only groups of insects with unequivocal quantitative evidence for numerous populations declines, while simultaneously serving as the most effective pollinators in temperate montane ecosystems (@cameron2020global, @goulson2008decline, @williams1982distribution, @colla2012assessing, @bergman1996micrometeorological, @bingham1998efficient). *Heterogeneous montane ecosystems simultaneously represent one of the most ecologically resilient areas in the temperate and oftentimes offer the sole potential refugia for multiple dimensions of biodiversity under climate change, whilst experiencing the most abrupt changes in mean annual temperature (CITE). An immediate understanding of how to manage previously overlooked keystone insect species, such as bumble bees, is essential if these refugial ecosystemn services are to be utilized while maintaining their current species richness.*

@@

```{r Sequence and Morphological Vouchers, out.width = "65%", echo = F,  fig.cap="A caption"}
knitr::include_graphics("../graphics/plots/rmbl_draft_tree.png")
```

*note this figure is draft mode, i reached out to C.H. Cole to get the official APG colors so we are gonna colour edges with that, I have also drawn phylo pics for almost all the labelled order and need to add them in !*

@@

The first date of modeled snow melt in the Gothic area (n = 17, $\bar{x}$ = 137.9, Mdn = 135, 3rd quantile = 151), and the first date of a consistent winter snow base (n = 17, $\bar{x}$ = 299.9, Mdn = 300, 1st quantile = 291) from 2000-2017, were used as delimiters for the inclusions of herbarium records in modelling. Of the **500** species predicted likely present in the area via logistic regression, 332 species (64.4%) with more than 10 records in the focal level 4 ecoregions ($\bar{x}$ = 35.01657, Mdn = 35, max = 96) had weibull estimates calculated, an additional 56 species (11.2%) with enough contributing records from the "Sedimentary Mid-Elevation Forests", a large ecoregion in general just beneath the elevation bands occupied by the five ecoregions around the study area had weibull estimates also calculated ($\bar{x}$ = 13.86885, Mdn = 13, max = 24).

@@

Appendix XX - Molecular Reference Specimen Table (con't)

@@

Appendix XX - All Species in the Sequence Databases (con't)

@@

Appendix XX - All Pollen Reference Slides Used to Establish Morphotypes (con't)

@@

Appendix XX - Models used for Species Distribution Model Ensembles
